SAT Competition 2020\tnoteref{title}

### 2021-02-04 paper/main.tex
added examples for il track

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. \textcolor{red}{Could mention concrete applications here?}
``Incremental'' here refers to the 
idea that
the individual calls to the SAT solver are not independent, but may share 
a common subset of the input clauses or differ in the presence of additional 
unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}.

>>>>

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a back-end solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. 
``Incremental'' here refers to the idea that the individual calls to the SAT solver are not independent, but may share a common subset of the input clauses or differ in the presence of additional unit clause assumptions~\cite{Nadel:2014:Incremental,Fazekas:2019:IncrementalInprocessing}. 
Examples for applications of incremental SAT solving are Counter-Example Guided Abstraction Refinement (CEGAR) based approaches, e.g., for Bounded Model Checking~\cite{Strichman:2005:ARBMC}, SAT-based Planning~\cite{Balyo:2017:IncrPlanning} or SAT Modulo Theories (SMT) solvers~\cite{Brummayer:2009:Boolector}.
